Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-06-04 paper/main.tex
Auto Update from local Sharelatex

In the health care domain in the United States the key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA). HIPAA is backed by significant civil penalties as well as specifics about security and what can and cannot be done with protected health information \cite{hippaviol}. There are two primary methods by which data can be shared or made public: de-identifcation, the removal of specific identifiers or summarization to a level at which individual identification is minimized, and through strict legal relationships called a business associate agreement. Even institutions which share data within the confines of the laws face a steep institutional risk. These legal barriers makes it difficult to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.

@@

% continue re-writing from here
These rules are ultimately good for citizens, but they create a pickle for scientists studying humans as it's very difficult to follow normal processes in scientific rigor while complying with privacy protection rules.

@@

% previously had some information about various data anonymization and synthesis techniques. Put that back?

@@

KFP provides a unique contirbution to the space of reproducible machine learning. Through providing ad-hoc faux data, machine learning researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux data derived from private data. However, there are several areas that could be improved or researched further: improved code sharing, addressing minimum dataset size issues, and evaluation of this system in a machine learning workflow.

While we have provided software code and a description of our methods in our GitHub repository, we believe that computational reproducibility should go beyond just making source code available. Peng recommends making code available in any form as an excellent first step towards reproducible research; the next step is to make code available "in a durable non-proprietary format" \cite{peng_reproducible_2011}. This is a level of code sharing rarely achieved in machine learning research. Currently there is no standard long term format that works for all computational environments. For the Python ecosystem however, the standard for sharing code is via a package on Python Package Index (PyPI). We intend to continue this resesarch to make KFP available as a Python package.

Another area that is open for further research is that of privacy protection through use of minimum dataset size. In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009}. However, it is not clear that these methods are approiate for use machine learning in general or the specific domain of health care. Futhermore, effect size and probability to detect specific effects may vary by use case. Thus, in this work, no attempt has been made to constrain data set sizes or results returned. KFP could be modified to return no results if a minimum threshold is not met based on the risk profile of the data owner or, alternatively, data boosting techniques in combination with data synthesis could be used.

The last area recommended for further research is to deploy and observe the use of KFP in an active machine learning environment where researchers are working with sensitive datasets. A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store. Additionally, as no private data was distributed via this system, actual review by security and compliance groups or IRBs may uncover additional requirements to reduce risk of data exposure that could require signicficant rework or futher study.

>>>>

In the health care domain in the United States the key law governing health data is the Health Insurance Portability and Accountability Act (HIPAA). HIPAA is backed by significant civil penalties as well as specifics about security and what can and cannot be done with protected health information \cite{hippaviol}. There are two primary methods by which data can be shared or made public: de-identification, the removal of specific identifiers or summarization to a level at which individual identification is minimized, and through strict legal relationships called a business associate agreement. Even institutions which share data within the confines of the laws face a steep institutional risk. These legal barriers makes it difficult to enable independent verification of machine learning (ML) models which often require enormous amounts of training data.

@@

The current legal environment creates a difficult situation for scientists in the health care domain. Early examples of re-identification attacks \cite{sweeney_2002} have have created apprehension on the part of businesses and legal experts in data sharing \cite{ohm_broken_2009}. Getting access to source health care data is slow and isn't always granted \cite{hodge_legal_1999, committee_hipaa_privacy_rule_2009}. More recently, research in the data sharing/privacy protection space has focused more on synthesis techniques such as in the case of the Synthea system, a tool to generate an entire outpatient Electronic Health Record (EHR) based on population statistics \cite{walonoski_synthea_2018}. Current solutions are not without their drawbacks however as they frequently require significant configuration of metadata before they can generate data or they attempt to solve the entire solution space and consequently are very slow to run.

@@

@@

KFP provides a unique contribution to the space of reproducible machine learning. Through providing ad-hoc faux data, machine learning researchers can have lower barriers to accessing private data as well as reduced barriers to sharing faux data derived from private data. However, there are several areas that could be improved or researched further: improved code sharing, addressing minimum dataset size issues, and evaluation of this system in a machine learning workflow.

While we have provided software code and a description of our methods in our GitHub repository, we believe that computational reproducibility should go beyond just making source code available. Peng recommends making code available in any form as an excellent first step towards reproducible research; the next step is to make code available "in a durable non-proprietary format" \cite{peng_reproducible_2011}. This is a level of code sharing rarely achieved in machine learning research. Currently there is no standard long term format that works for all computational environments. For the Python ecosystem however, the standard for sharing code is via a package on Python Package Index (PyPI). We intend to continue this research to make KFP available as a Python package.

Another area that is open for further research is that of privacy protection through use of minimum dataset size. In the field of education, statistical methods for calculating sample size based on probability of detecting a specific effect size are commonly used \cite{naep_2009}. However, it is not clear that these methods are appropriate for use machine learning in general or the specific domain of health care. Furthermore, effect size and probability to detect specific effects may vary by use case. Thus, in this work, no attempt has been made to constrain data set sizes or results returned. KFP could be modified to return no results if a minimum threshold is not met based on the risk profile of the data owner or, alternatively, data boosting techniques in combination with data synthesis could be used.

The last area recommended for further research is to deploy and observe the use of KFP in an active machine learning environment where researchers are working with sensitive datasets. A key limitation that may be identified is that of performance characteristics, particularly in a multi-user setting against a large relational database store. Additionally, as no private data was distributed via this system, actual review by security and compliance groups or institutional review boards may uncover additional requirements to reduce risk of data exposure that could require significant rework or further study.
